\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-26 manuscript.tex
edits
Citations are showing up as ?’s and not sure why

\clearpage
\footnotetext{\flushleft{Manuscript received \line(1,0){120};   revision accepted\line(1,0){120}.}
\vspace*{1cm}
\subsection*{Acknowledgements}
Place brief acknowledgments, if desired, as a separate paragraph, using the following style: “The author(s) thank(s)…”. For brevity, do not use first names. Include grant acknowledgments here.
}

@@

%TO DO
%check citations in last paragraph for ter1
%reformat for AJB
%preprint somewhere
%finish fixing paragraph that jeff doesn't like
%check map details
%Code for SAS and command line stuff on Git
%Phenotyping on Figshare http://dx.doi.org/10.6084/m9.figshare.776926 -- do we need to cite this in the manuscript somewhere?

@@

Domesticated crops and their wild progenitors provide an excellent system in which to study adaptation and genomic changes associated with human-mediated selection \citep{Ross-Ibarra2007}. Perhaps the central focus of the study of domestication has been the identification of genetic variation underlying agronomically important traits such as fruit size and plant architecture \citep{OlsenGross2010}. Additionally, many domesticates show reduced genetic diversity when compared to their wild progenitors, and an understanding of the distribution of diversity in the wild and its phenotypic effects has become increasingly useful to crop improvement \citep{KovachMcCouch2008}. But while some effort has been invested into understanding how wild alleles behave in their domesticated relatives \citep[e.g.][]{Bai2007}, very little is known about the role that alleles found most commonly in domesticates play in natural populations of their wild progenitors \citep{Whitton1997}.

>>>>

\clearpage
\footnotetext{\flushleft{Manuscript received \line(1,0){120};   revision accepted\line(1,0){120}.}
\vspace*{1cm}
\subsection*{Acknowledgements}
We would like to thank the Department of Plant Sciences at UC Davis for Graduate Student Research funding to LEV, \lev{Matt UC Mexus}, and G. Coop for helpful discussion.

@@

%TO DO
%check citations in last paragraph for ter1

%preprint somewhere
%finish fixing paragraph that jeff doesn't like
%check map details
%Code for SAS and command line stuff on Git
%Phenotyping on Figshare http://dx.doi.org/10.6084/m9.figshare.776926 -- do we need to cite this in the manuscript somewhere?

@@

\lev{So the citations are showing up as ?'s now}
Domesticated crops and their wild progenitors provide an excellent system in which to study adaptation and genomic changes associated with human-mediated selection \citep{Ross-Ibarra2007}. Perhaps the central focus of the study of domestication has been the identification of genetic variation underlying agronomically important traits such as fruit size and plant architecture \citep{OlsenGross2010}. Additionally, many domesticates show reduced genetic diversity when compared to their wild progenitors, and an understanding of the distribution of diversity in the wild and its phenotypic effects has become increasingly useful to crop improvement \citep{KovachMcCouch2008}. But while some effort has been invested into understanding how wild alleles behave in their domesticated relatives \citep[e.g.][]{Bai2007}, very little is known about the role that alleles found most commonly in domesticates play in natural populations of their wild progenitors \citep{Whitton1997}.
